Exposing Disputed Statements on the Web

### 2009-03-28 papers/uist_thinklink/thinklink.tex
Folded in Tye suggestions

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed on presents only one side of a contentious issue. As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.

All information in Think Link is provided by users. Think Link is designed to cator to two usage scenarios. Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with. Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.

@@

\keywords{CSCW, Sensemaking, Annotation, Argumentation, Web}

@@

The web contains a huge amount of information, but but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. If a user is to gain a broad understanding ofa topic then they will need to either stick to sources that they trust or spend time looking for information on other web sites that conflicts with what they have read. Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.

In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view. When Think Link is used as a browser plugin it will highlight text that makes a disputed claim. If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by the voting of other Think Link users (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two distinct groups of people. Activists care strongly about particular claims that they disagree with and combine Think Link with a preferred search engine to find instances of these claims and mark them up so other users can see them. Sceptical readers install Think Link as a browser plugin so that they can see when things they read are disputed and find other links that present other points of view. A reader may be an activist for one issue and a sceptical reader for others.

@@

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments around an issue as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2006} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987a} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

Prior IBIS tools have been intended for conflict modelling and resolution: users build up a complex graph modelling an issue and then use this graph to decide what to do. By contrast Think Link uses an IBIS graph for conflict discovery and evidence identification. In a tool like gIBIS a user is encouraged to break down their argument into as much detail as possible and encouraged to use the graph itself to reach a decision. By contrast, in Think Link a user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form their opinion primarily by reading the articles that have been linked as evidence. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit the expected usage for other IBIS tools.

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.

Cohere~\cite{Shum2008} is perhaps the IBIS tool most similar to Think Link. Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses. While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways. In Cohere, a user attaches a web snippet to their idea in order to use it as evidence. By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument. More generally,

More generally, a key way Think Link differs from Cohere is that it separates the creation of claims from their association with snippets. A user can mark a snippet without yet being sure what claims it should be linked to, or can mark a claim without knowing what snippets other users will associate with it.

Think Link uses a simple IBIS-style graph structure in which claims support, oppose, or relate-to other claims. Several alternative graph structures have been proposed for describing arguments and design rationale. WinWin~\cite{Boehm2006} models the different stakeholders and their different motives. The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions. QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions. More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.

When choosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use. For Think Link, we tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model. The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not. FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. Think Link's database automatically imports all contentious claims identified by Snopes.

@@

Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004} allow users to highlight sections of text on a page. Annotation systems often also do clipping. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. In some cases, other users who see a web page an see text highlighted where other users have clipped it.

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly document with logical triples (subject, verb, object) describing interesting claims that are being made in the document. This semantic information can be used to connect claims in different documents and see when a logical claim in one document contradicts another. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.

Videolyzer~\cite{Diakopoulos2008} allows users to annotate and comment on political videos with accompanying textual transcriptions. A user can mark up a section of video for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made.

@@

@@

If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim being true, as determined by the user community (Figure~\ref{claimview}).

@@

Once a user has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.

In our user studies, we found that users wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim, then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

@@

We found that it was important to allow the claim browser interface to be used in two different ways. When a user is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are four types of node: snippets, claims, topics, and users. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A claim can support,oppose, or relate-to another claim, a claim can relate-to a topic, and a topic can relate-to another topic. This is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, and we allow a claim to simply relate-to another claim, rather than having to either support or oppose it.

Think Link uses topics to group together related claims. A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''. Think Link uses the list of page titles on Wikipedia as a seed-set for its topics.

The panel for a claim lists evidence that will help a user decide whether the claim is true. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support the truth of this claim.

@@

One danger in a voting system is that a large group of people will drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. Of course, these techniques only work to a limited extent, and so we expect that editorial moderation may be needed for highly controversial topics, as it is in Wikipedia.

@@

If a user has installed the Think Link browser extension then they can create a snippet from text on a web page by selecting the text and selecting either ``This is disputed'' or ``This is interesting'' from the context menu. A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful information that would be useful to readers investigating a disputed claim.

@@

Think Link does not require that a user associate a snippet with a snippet at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. One anticipated usage scenario for Think Link is an activist user who users a search engine to find a large number of snippets that make a clam that the user disagrees with. In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.

@@

\begin{description}
\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}). A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates to'' link types. If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.

@@

\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a snippet (Figure~\ref{sniptopic}). If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet. As with the snippet suggested, a user can guide the suggestions by entering keywords. If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.

@@

When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim. It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to offer support for a particular claim. In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for. In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.

Think Link uses the Wikify! algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia pages and predicts what pages that text would be most likely to link to, based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that a heavily linked to.

@@

As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected. If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together.

@@

Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.

@@

We performed two qualitative ``think aloud'' user studies. The aim of these studies was to inform the development of Think Link. The studies were not intended to validate the design of Think Link as being correct. Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different points. To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. We present the results of the two studies together.

@@

For the first study we recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the Internet to find information. We recruited participants using a posting to the Craigslist.org classified advert site. In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

@@

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

For the second study, we recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case). The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).

Participants were shown the prototype interface shown in Figure~\ref{secondbrowser}. This is similar to the interface described earlier in this paper, but uses drag and drop to make connections, rather than a suggestion system.

@@

Participants liked the ability to see when other pages disagreed with the claim they were looking at. One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive''.

@@

Some users wanted to associate a snippet with a topic but without associating it with a specific claim. For example, they might find the text of an important speech, or the results of a sporting event. While it is possible that they might want to use this as evidence for a claim in the future, they didn't want to have to decide what the claim was immediately. In the final interface one can associate a snippet with a topic rather than a claim.

@@

Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information? In the final interface, users can choose how specific to make their claims after they have gathered a large number of snippets and know what information is repeated between sources.

Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they they could make the dialog go away. Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet. The final interface avoids this problem by allowing a used to delay the association of a claim for a snippet until they know what useful claim they want to use that snippet as evidence for.

>>>>

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed. As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.

All information in Think Link is provided by users. Think Link is designed to support two usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.

@@

\keywords{Sensemaking, Annotation, Argumentation, Web, CSCW}

@@

The web contains a huge amount of information, but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read. Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view. When Think Link is used as a browser plugin it will highlight text that makes a disputed claim (Figure~\ref{highlight}). When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim, as voted for by other Think Link users (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two groups of people:

\begin{description}
\item[Activists] care strongly about particular issues. They use Think Link to find and mark instances of claims that this disagree with so that other readers will see that these claims are disputed and be exposed to the opposing point of view.

\item[Sceptical Readers] want to know when information they read is disputed. They install Think Link as a browser plugin so that it will highlight disputed claims and show them the best evidence supporting opposing points of view.
\end{description}

@@

Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark a claim as supporting or opposing another claim, and allow one to mark an claim as relating to an issue.

Although Think Link's argument graph is very similar to that used by IBIS tools, it uses it for a different purpose. In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view. A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form an opinion primarily by looking at the snippets that make that claim, rather than by looking at the argument graph itself. This differs from the normal way in which previous IBIS tools have been used. In a tool such as gIBIS~\cite{Conklin1987a} the focus is on the argument graph. A user is encouraged to break their argument down into as many separate ideas as possible and a user is expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many topics --- this would not fit with the expected usage model for other IBIS tools.

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their dispute, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.

Cohere~\cite{Shum2008} allows a user to associate a web page with a claim in an argument graph and provides a Firefox plugin to help users do this; however Cohere and Think Link have very different models. In Cohere, when one creates a new claim one can specify one or more URLs to be used as supporting evidence. Cohere is not intended to be used as a tool to identify disputed snippets, and does not expect users to attach large numbers of web snippets to existing claims.

Think Link uses a simple IBIS-like graph structure in which claims support, oppose, or relate-to other claims. Several alternative graph structures have been proposed for describing arguments and design rationale. WinWin~\cite{Boehm2006} models the different stakeholders and their different motives. The Toulmin Model~\cite{toulmin1958} breaks down the logical way in which arguments are formed from evidence, rules, and exceptions. QOS~\cite{Maclean1991} explicitly states the criteria used to choose between positions. More formal models such as Carneades~\cite{Gordon2007} have been used for artificial intelligence.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not. FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. Think Link's database automatically imports all contentious claims identified by Snopes. FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.

@@

Annotation tools~\cite{Marshall1998} such as Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004} allow users to highlight sections of text on a page. Annotation systems often also do clipping. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998}, Hunter Gatherer~\cite{Schraefel2002}, ScratchPad~\cite{Gotz2007}, ClipMarks\footnote{http://clipmarks.com}, and Diigo\footnote{http://diigo.com} allow users to collect text snippets from web pages, tag them, and share them with friends. In some cases, other users who see a web page an see text highlighted where other users have clipped it. These tools do not attempt to identify when snippets make disputed claims or to connect them to opposing sides of an argument.

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly paper with logical triples (subject, verb, object) describing interesting claims that are being made in the document. This semantic information can be used to connect claims in different documents. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents. Unlike Think Link, these tools are looking for logical relations between entities rather than instances of already-known claims.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos with accompanying textual transcriptions. A user can mark up a section of video for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempty to gather multiple video sections that make a common contentious claim.

\todo{Ask Nicholas if he would like to read the paper}

@@

If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim, where best is determined by the number of users who voted for that evidence (Figure~\ref{claimview}).

@@

Once a sceptical reader has identified a claim that they are interested in, they can use Think Link's claim browser interface (Figure~\ref{panels}) to investigate the evidence for and against it, and to see what other contentious claims have been made about related issues.

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

The panel for a claim (Figure~\ref{panel}) lists evidence that will help a user decide whether the claim is true. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.

@@

We found that it was important to allow the claim browser interface to be used in two different ways. When a sceptical reader is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of node: snippets, claims, and topics. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Think Link uses topics to group together related claims. A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''. Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.

Think Link's graph model is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting topics together and four ways of connecting a claim to an topic into a single relates-to relation. The result is a graph structure that is significantly simpler. While Think Link's graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of link and node types reduces the mential effort required to create an argument graph.

@@

One danger in a voting system is that a large group of people will drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.

@@

If a user has installed the Think Link browser extension then they can create a snippet from text on a web page by selecting the text and selecting either ``This is disputed'' or ``This is interesting'' from the context menu. A user selects ``This is disputed'' if they believe that readers of that snippet should be alerted of the fact that a claim that that snippet is making or implying is disputed. A user selects ``This is interesting'' if they believe that the snippet contains useful evidence that could be for readers investigating a disputed claim.

@@

Think Link does not require that a user associate a snippet with a claim at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a clam that they disagrees with. In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.

@@

\begin{description}
\item[Claim first:] If a user navigates to a claim and clicks the ``add snippet'' button, Think Link will suggest unattached snippets that the user created recently and that are textually similar to the wording of the claim or other snippets currently attached to the claim (Figure~\ref{snipclaim}). A user can attach a suggested snippet to the claim by clicking on icons representing ``supports'', ``opposes'', or ``relates-to'' link types. If Think Link does not suggest the right snippets then Think Link can guide the suggestions by entering keywords into the text box above the suggestion list.

@@

\item[Snippet first:] If a user selects the ``unfiled'' tab at the top of the claim browser then Think Link will show a list of all the snippets that they have marked but not yet associated with a claim or a topic (Figure~\ref{sniptopic}). If the user selects an unfiled snippet then Think Link will suggest claims or topics that the user might want to associate with that snippet. As with the claim-first method, a user can guide the suggestions by entering keywords. If the correct claim is not suggested then the user can create a new claim by typing it into the text box and clicking the ``add'' button.

@@

When gathering ``interesting'' snippets, a user may want to associate a snippet with a general topic rather than a specific claim. It is only necessary to associate an ``interesting'' snippet with a claim when a user wants to use it as evidence for a particular claim. In some cases a user will gather snippets that they might want to use later, but without concrete plans for how they might want to use them or what claims they might want to use them as evidence for. In such cases, it is easier to file the interesting snippets under a general topic and possibly attach them to a claim some time in the future.

As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected. If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to connect them with a single click. Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.

Think Link uses the Wikify algorithm~\cite{Mihalcea2007} to suggest topics for snippets or claims. The Wikify algorithm imagines that a piece of text was on a Wikipedia page and predicts what pages that text would most likely link to based on the probability that any particular n-gram links to any particular page. Recall that the set of Think Link topics is seeded with the set of Wikipedia page titles. The Wikify algorithm performs significantly better than a word-frequency comparison as it biases towards topics that are heavily linked to.

Even with these suggestion and bulk connection features, gathering snippets that make a disputed claim or provide useful evidence requires a non-trivial amount of work. Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog. Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to be notified every time a new page appears about the issue they are interested in. Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achive useful coverage by only marking up the relatively small number of very popular pages (for example articles on major news sites).

@@

@@

@@

We performed two qualitative ``think aloud'' user studies. The aim of these studies was to inform the development of Think Link. The studies were not intended to validate the design of Think Link as being correct. Think Link is designed to be used by a large number of users gathering a vast amount of evidence for many different claims. To confidently state that our design was successful we would need to be able to test Think Link on a much greater scale than we currently have resources for.

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. At the end of each study, we asked each partipicant whether there were times in the past where they would have wanted to use Think Link. We present the results of the two studies together.

\todo{Say something about final informal evaluation}
%After the second study, we made minor changes to our user interface (described below) and performed an informal user study with people in our organization to

@@

For the first study we recruited 12 paid participants, 5 female, 7 male, aged 18 to 52. Nine participants regularly posted to a blog and the other three regularly posted comments to blogs or mailing lists. Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentry) and said they regularly shared information with friends. We avoided applications from people who were more interested in less disputed topics like social networking or sport.

\todo{Get the correct number of bloggers}

@@

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use

the web sites they normally normally and use Think Link to identify snippets that made claims they thought were interesting or disputed and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

For the second study, we recruited 6 paid participants, 4 female, 2 male. Four participants had a blog. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the local university semester meant that five of the participants were college students.

In the second study we were more confident about the usability of our tool and so we decided to tell the participants nothing about how to use it. We gave each user a brief description of the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw (the ``sceptical reader'' use case). The second task was to identify disputed claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with (the ``activist'' use case).

Participants were shown the prototype interface shown in Figures~\ref{secondbrowser} and \ref{secondsnippetbox}. This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, and it required a user to choose a claim at the point at which they create a snippet.

@@

Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would want to marking up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. One participants said they found the tool ``very intuitive''.

@@

Some users wanted to associate a snippet with a topic but without associating it with a specific claim. For example, they might find the text of an important speech, or the results of a sporting event. While it is possible that they might want to use this as evidence for a claim in the future, they didn't want to have to decide what the claim was immediately. In the final interface one can choose to associate a snippet with a topic.

@@

Several users expressed confusion about how specific the claim made by a snippet should be, or when they should pick an existing claim rather than create a new one. For example, if a snippet says ``Global temperatures will rise by X degrees by 2050'' then is that making the claim ``Global temperatures will rise'', or should a new claim be created that contains the extra information? In the final interface, users are expected to only create a claim when they have several snippets that make the same claim. This makes it easier to know how broad the claim should be as they know how much information is shared by claims.

Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they they could make the dialog go away. Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet. The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and have a particular disputed claim in mind.
